---
title: "CS2_MD"
author: "Varun Gopal"
date: '2022-04-16'
output: html_document
---

By Varun Gopal

This presentation investigates factors related to attrition. In addition, machine learning models were used to attempt to predict employee attrition and salary. Finally, factors related to job role were examined.

Importing packages and dataset
```{r, message=FALSE,warning=FALSE}
#Libraries
library(GGally)
library(tidyverse)
library(formattable)
library(plotly)
library(class)
library(caret)
library(e1071)
library(randomForest)
library(varImp)

#Import dataset
CS2=read.csv(file.choose(),header=T)
```

Investigating categorical variables
```{r}
#Make Attrition a factor
CS2$Attrition=as.factor(CS2$Attrition)

#Split Data into continuous vs categorical data
CS2cont=data.frame(rows=1:dim(CS2)[1]) #Build empty dfs
CS2cat=data.frame(rows=1:dim(CS2)[1])
#Fill in CS2cont with all 'int' types excluding those on scale of 1-5 or 1-10
for(i in 1:dim(CS2)[2]){
  if(class(CS2[,i])=='integer' & length(levels(as.factor(CS2[,i])))>5){
    CS2cont=cbind(CS2cont,CS2[i])
  } else{
    CS2cat=cbind(CS2cat,CS2[i])
  }
}

#Clean up columns and add attrition to CS2cont
CS2cont=CS2cont%>%select(!rows)
CS2cont$Attrition=CS2$Attrition
CS2cat=CS2cat%>%select(!rows)

#Loop to make all columns in CS2cat factors
for (i in 1:dim(CS2cat)[2]){
  CS2cat[,i]=as.factor(CS2cat[,i])
}

#INVESTIGATING CATEGORICAL VARIABLES

#Determine percent attrition based on business travel
BizTravel=as.data.frame(CS2cat%>%group_by(BusinessTravel)%>%summarize(total=n()))
BizTravelAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(BusinessTravel)%>%summarize(num_yes=n()))
BizTravel=merge(BizTravel,BizTravelAttr,by='BusinessTravel')
BizTravel$Percent_Attrition=BizTravel$num_yes/BizTravel$total
colnames(BizTravel)[c(1,4)]=c('Frequency of Business Travel','Percent Attrition')
formattable(BizTravel[,c(1,4)])

#Determine percent attrition based on department
Dep=as.data.frame(CS2cat%>%group_by(Department)%>%summarize(total=n()))
DepAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(Department)%>%summarize(num_yes=n()))
Dep=merge(Dep,DepAttr,by='Department')
Dep$Percent_Attrition=Dep$num_yes/Dep$total
colnames(Dep)[c(1,4)]=c('Department','Percent Attrition')
formattable(Dep[,c(1,4)])

#Determine percent attrition based on years of education
Edu=as.data.frame(CS2cat%>%group_by(Education)%>%summarize(total=n()))
EduAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(Education)%>%summarize(num_yes=n()))
Edu=merge(Edu,EduAttr,by='Education')
Edu$Percent_Attrition=Edu$num_yes/Edu$total
colnames(Edu)[c(1,4)]=c('Years Studying','Percent Attrition')
formattable(Edu[,c(1,4)])

#Determine percent attrition based on education field
EduF=as.data.frame(CS2cat%>%group_by(EducationField)%>%summarize(total=n()))
EduFAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(EducationField)%>%summarize(num_yes=n()))
EduF=merge(EduF,EduFAttr,by='EducationField')
EduF$Percent_Attrition=EduF$num_yes/EduF$total
colnames(EduF)[c(1,4)]=c('Field of Study','Percent Attrition')
formattable(EduF[,c(1,4)])

#Determine percent attrition based on Environmental Satisfaction
EnvSat=as.data.frame(CS2cat%>%group_by(EnvironmentSatisfaction)%>%summarize(total=n()))
EnvSatAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(EnvironmentSatisfaction)%>%summarize(num_yes=n()))
EnvSat=merge(EnvSat,EnvSatAttr,by='EnvironmentSatisfaction')
EnvSat$Percent_Attrition=EnvSat$num_yes/EnvSat$total
colnames(EnvSat)[c(1,4)]=c('Environmental Satisfaction','Percent Attrition')
formattable(EnvSat[,c(1,4)])

CS2cat%>%ggplot(aes(x=Education,fill=Attrition))+
  geom_bar()

#Determine percent attrition based on Gender
Gender=as.data.frame(CS2cat%>%group_by(Gender)%>%summarize(total=n()))
GenderAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(Gender)%>%summarize(num_yes=n()))
Gender=merge(Gender,GenderAttr,by='Gender')
Gender$Percent_Attrition=Gender$num_yes/Gender$total
colnames(Gender)[c(1,4)]=c('Gender','Percent Attrition')
formattable(Gender[,c(1,4)])

#Determine percent attrition based on Job Involvement
JobInv=as.data.frame(CS2cat%>%group_by(JobInvolvement)%>%summarize(total=n()))
JobInvAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(JobInvolvement)%>%summarize(num_yes=n()))
JobInv=merge(JobInv,JobInvAttr,by='JobInvolvement')
JobInv$Percent_Attrition=JobInv$num_yes/JobInv$total
colnames(JobInv)[c(1,4)]=c('Job Involvement','Percent Attrition')
formattable(JobInv[,c(1,4)])

#Determine percent attrition based on Job Level
JobLvl=as.data.frame(CS2cat%>%group_by(JobLevel)%>%summarize(total=n()))
JobLvlAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(JobLevel)%>%summarize(num_yes=n()))
JobLvl=merge(JobLvl,JobLvlAttr,by='JobLevel')
JobLvl$Percent_Attrition=JobLvl$num_yes/JobLvl$total
colnames(JobLvl)[c(1,4)]=c('Job Level','Percent Attrition')
formattable(JobLvl[,c(1,4)])

#Determine percent attrition based on Job Role
Role=as.data.frame(CS2cat%>%group_by(JobRole)%>%summarize(total=n()))
RoleAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(JobRole)%>%summarize(num_yes=n()))
Role=merge(Role,RoleAttr,by='JobRole')
Role$Percent_Attrition=Role$num_yes/Role$total
colnames(Role)[c(1,4)]=c('Job Role','Percent Attrition')
formattable(Role[,c(1,4)])

#Determine percent attrition based on Job Satisfaction
JobSat=as.data.frame(CS2cat%>%group_by(JobSatisfaction)%>%summarize(total=n()))
JobSatAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(JobSatisfaction)%>%summarize(num_yes=n()))
JobSat=merge(JobSat,JobSatAttr,by='JobSatisfaction')
JobSat$Percent_Attrition=JobSat$num_yes/JobSat$total
colnames(JobSat)[c(1,4)]=c('Job Satisfaction','Percent Attrition')
formattable(JobSat[,c(1,4)])

#Determine percent attrition based on Marital Status
Married=as.data.frame(CS2cat%>%group_by(MaritalStatus)%>%summarize(total=n()))
MarriedAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(MaritalStatus)%>%summarize(num_yes=n()))
Married=merge(Married,MarriedAttr,by='MaritalStatus')
Married$Percent_Attrition=Married$num_yes/Married$total
colnames(Married)[c(1,4)]=c('Marital Status','Percent Attrition')
formattable(Married[,c(1,4)])

#Determine percent attrition based on Overtime
OT=as.data.frame(CS2cat%>%group_by(OverTime)%>%summarize(total=n()))
OTAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(OverTime)%>%summarize(num_yes=n()))
OT=merge(OT,OTAttr,by='OverTime')
OT$Percent_Attrition=OT$num_yes/OT$total
colnames(OT)[c(1,4)]=c('Overtime','Percent Attrition')
formattable(OT[,c(1,4)])

#Determine percent attrition based on Performance Rating
PR=as.data.frame(CS2cat%>%group_by(PerformanceRating)%>%summarize(total=n()))
PRAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(PerformanceRating)%>%summarize(num_yes=n()))
PR=merge(PR,PRAttr,by='PerformanceRating')
PR$Percent_Attrition=PR$num_yes/PR$total
colnames(PR)[c(1,4)]=c('Performance Rating','Percent Attrition')
formattable(PR[,c(1,4)])

#Determine percent attrition based on Relationship Satisfaction
RelSat=as.data.frame(CS2cat%>%group_by(RelationshipSatisfaction)%>%summarize(total=n()))
RelSatAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(RelationshipSatisfaction)%>%summarize(num_yes=n()))
RelSat=merge(RelSat,RelSatAttr,by='RelationshipSatisfaction')
RelSat$Percent_Attrition=RelSat$num_yes/RelSat$total
colnames(RelSat)[c(1,4)]=c('Relationship Satisfaction','Percent Attrition')
formattable(RelSat[,c(1,4)])

#Determine percent attrition based on Stock Option Level
StockLvl=as.data.frame(CS2cat%>%group_by(StockOptionLevel)%>%summarize(total=n()))
StockLvlAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(StockOptionLevel)%>%summarize(num_yes=n()))
StockLvl=merge(StockLvl,StockLvlAttr,by='StockOptionLevel')
StockLvl$Percent_Attrition=StockLvl$num_yes/StockLvl$total
colnames(StockLvl)[c(1,4)]=c('Stock Option Level','Percent Attrition')
formattable(StockLvl[,c(1,4)])

#Determine percent attrition based on Work Life Balance
WLB=as.data.frame(CS2cat%>%group_by(WorkLifeBalance)%>%summarize(total=n()))
WLBAttr=as.data.frame(CS2cat%>%filter(Attrition=='Yes')%>%group_by(WorkLifeBalance)%>%summarize(num_yes=n()))
WLB=merge(WLB,WLBAttr,by='WorkLifeBalance')
WLB$Percent_Attrition=WLB$num_yes/WLB$total
colnames(WLB)[c(1,4)]=c('Work Life Balance','Percent Attrition')
formattable(WLB[,c(1,4)])
```

Investigating continuous variables
```{r}
#INVESTIGATE CONTINUOUS VARIABLES

#Comparing attrition with age, dailyrate, and distancefromhome
CS2cont[,c(17,2,3,4)]%>%ggpairs()

#Comparing attrition with hourlyrate, monthlyincome, and monthlyrate
CS2cont[,c(17,6,7,8)]%>%ggpairs()

#Comparing attrition with numcompaniesworked, percentsalaryhike, and totalworkingyears
CS2cont[,c(17,9,10,11)]%>%ggpairs()

#Comparing attrition with trainingtimeslastyear, yearsatcompany, and yearsincurrentrole
CS2cont[,c(17,12,13,14)]%>%ggpairs()

#Comparing attrition with yearssincelastpromotion and yearswithcurrmanager
CS2cont[,c(17,15,16)]%>%ggpairs()

CS2%>%select(Attrition,JobRole,YearsAtCompany,YearsInCurrentRole,TotalWorkingYears)%>%ggpairs()

CS2%>%ggplot(aes(x=YearsAtCompany,y=YearsInCurrentRole,col=Attrition))+
  geom_point()
```

Testing Models
```{r}
#TESTING MODELS

#Cleaning up CS2
CS2clean=CS2%>%select(!(ID|EmployeeCount|EmployeeNumber|Over18|StandardHours))

#Create Training and Test Split
seednum=sample(1:100000,1)#seed number
set.seed(seednum)#Random seed
TrainInd=sample(1:dim(CS2)[1],round(0.7*dim(CS2)[1]))#Sample of 70% of total values
AttrTrain=CS2clean[TrainInd,]#Random 70% of CS2 put into training set
AttrTest=CS2clean[-TrainInd,]#Random 30% of CS2 put into test set

SpecMatrix=matrix(nrow=1000,ncol=2)
colnames(SpecMatrix)=c('Seed Number','Specificity')

#Loop to tune seed
for (i in 1:dim(SpecMatrix)[1]){
  set.seed(i)
  #Split CS2 into sets w/ Attrition=='Yes' and Attrition=='No'
  CS2Yes=CS2clean%>%filter(Attrition=='Yes')
  CS2No=CS2clean%>%filter(Attrition=='No')
  IndexYes=sample(1:dim(CS2Yes)[1],round(0.7*dim(CS2Yes)[1]))
  IndexNo=sample(1:dim(CS2No)[1],round(0.7*dim(CS2No)[1]))
  
  #Training/Test Splits Yes and No
  TrainYes=CS2Yes[IndexYes,]
  TestYes=CS2Yes[-IndexYes,]
  TrainNo=CS2No[IndexNo,]
  TestNo=CS2No[-IndexNo,]
  
  #Merge Training and Test Splits
  AttrTrain=rbind(TrainYes,TrainNo)
  AttrTest=rbind(TestYes,TestNo)
  
  #Run Machine Learning Models
  model=naiveBayes(Attrition~.,data=AttrTrain)
  AttrClass=predict(model,AttrTest)
  
  CM=confusionMatrix(table(AttrClass,AttrTest$Attrition))
  SpecMatrix[i,1]=i
  SpecMatrix[i,2]=CM$byClass['Specificity']
}
#Find the best seed out of 1000
SpecMatrix=as.data.frame(SpecMatrix)
SpecMatrix%>%filter(Specificity==max(Specificity))

#Stratified Training/Test Split
seednum=sample(1:100000,1)#seed number
hiseed=58 #Tuned seed
set.seed(hiseed)#Random seed

#Split CS2 into sets w/ Attrition=='Yes' and Attrition=='No'
CS2Yes=CS2clean%>%filter(Attrition=='Yes')
CS2No=CS2clean%>%filter(Attrition=='No')
IndexYes=sample(1:dim(CS2Yes)[1],round(0.7*dim(CS2Yes)[1]))
IndexNo=sample(1:dim(CS2No)[1],round(0.7*dim(CS2No)[1]))

#Training/Test Splits Yes and No
TrainYes=CS2Yes[IndexYes,]
TestYes=CS2Yes[-IndexYes,]
TrainNo=CS2No[IndexNo,]
TestNo=CS2No[-IndexNo,]

#Merge Training and Test Splits
AttrTrain=rbind(TrainYes,TrainNo)
AttrTest=rbind(TestYes,TestNo)

#Run Machine Learning Models
NBmodel=naiveBayes(Attrition~.,data=AttrTrain)
AttrClassNB=predict(NBmodel,AttrTest)
NBCM=confusionMatrix(table(AttrClassNB,AttrTest$Attrition))

RFmodel=randomForest(Attrition~.,data=AttrTrain,ntree=435)
AttrClassRF=predict(RFmodel,AttrTest)
RFCM=confusionMatrix(table(AttrClassRF,AttrTest$Attrition))

#Tuning ntree
RFSpec=data.frame(ntree=100:500,Specificity=NA)

for (i in 100:500){
  RFmodel=randomForest(Attrition~.,data=AttrTrain,importance=T,ntree=i)
  AttrClassRF=predict(RFmodel,AttrTest)
  RFCM=confusionMatrix(table(AttrClassRF,AttrTest$Attrition))
  RFSpec[(i-99),2]=RFCM$byClass['Specificity']
}
dim(RFSpec)
RFSpec%>%filter(Specificity==max(Specificity))
head(RFSpec)
```

Attempt at permutation feature importance. I tried to code in
feature shuffling, and I used balanced accuracy to measure impact on the model. However, I acknowledge that I may have made quite a few mistakes in both my code and my grasp of the concept. Regardless, this is my best attempt
```{r}
#After multiple attempts, naive Bayes was a better model than random forest


#permutation feature importance Naive Bayes
CS2perm=CS2clean%>%select(!Attrition)
CS2perm$Attrition=CS2clean$Attrition
AccDiff=matrix(nrow=30,ncol=2)

for (i in 1:(dim(CS2perm)[2]-1)){
  #seed for split
  set.seed(58)
  #Stratified Sample
  #70/30 train/test split based on Attrition='Yes'
  PermYes=CS2perm%>%filter(Attrition=='Yes')
  IndYes=sample(1:dim(PermYes)[1],round(0.7*dim(PermYes)[1]))
  PermYesTrain=PermYes[IndYes,]
  PermYesTest=PermYes[-IndYes,]
  
  #70/30 train/test split based on Attrition='No'
  PermNo=CS2perm%>%filter(Attrition=='No')
  IndNo=sample(1:dim(PermNo)[1],round(0.7*dim(PermNo)[1]))
  PermNoTrain=PermNo[IndNo,]
  PermNoTest=PermNo[-IndNo,]
  
  #Merge train/test
  PermTrain=rbind(PermYesTrain,PermNoTrain)
  PermTest=rbind(PermYesTest,PermNoTest)
  
  #Naive Bayes
  unshuffled=naiveBayes(Attrition~.,data=PermTrain)
  unshuffledClass=predict(unshuffled,PermTest)
  UCM=confusionMatrix(table(unshuffledClass,PermTest$Attrition))
  
  #Seed to shuffle
  seednum=sample(1:(dim(AccDiff)[1])^6,1)#Change this on every iteration for a different shuffle
  set.seed(seednum)
  #Shuffle Test Column
  PermTrain[,i]=sample(PermTrain[,i])
  
  set.seed(58)
  #Naive Bayes
  shuffled=naiveBayes(Attrition~.,data=PermTrain)
  shuffledClass=predict(shuffled,PermTest)
  SCM=confusionMatrix(table(shuffledClass,PermTest$Attrition))
  
  AccDiff[i,2]=UCM$byClass['Balanced Accuracy']-SCM$byClass['Balanced Accuracy']
  AccDiff[i,1]=colnames(CS2perm)[i]
}
AccDiff=as.data.frame(AccDiff)
colnames(AccDiff)=c('Shuffled_Feature','BADiff')
AccDiff%>%arrange(desc(BADiff))
seednum
```

Examining Overtime
```{r}
#Examine Overtime

#Compare Overtime to Age
CS2%>%ggplot(aes(x=OverTime,y=Age))+
  geom_boxplot()

#Compare Overtime to years in company
CS2%>%ggplot(aes(x=OverTime,y=YearsAtCompany))+
  geom_boxplot()

#Compare Overtime to years in current role
CS2%>%ggplot(aes(x=OverTime,y=YearsInCurrentRole))+
  geom_boxplot()

#Compare percent overtime to job role
RoleOT1=CS2%>%group_by(JobRole)%>%summarize(total=n())
RoleOT2=CS2%>%filter(OverTime=='Yes')%>%group_by(JobRole)%>%summarize(num_yes=n())
RoleOT=merge(RoleOT1,RoleOT2,by='JobRole')
RoleOT$PercentOT=RoleOT$num_yes/RoleOT$total
colnames(RoleOT)[c(1,4)]=c('Job Role','Percent Overtime')
formattable(RoleOT[,c(1,4)])
Role

#Compare percent overtime to department
DepOT1=CS2%>%group_by(Department)%>%summarize(total=n())
DepOT2=CS2%>%filter(OverTime=='Yes')%>%group_by(Department)%>%summarize(num_yes=n())
DepOT=merge(DepOT1,DepOT2,by='Department')
DepOT$PercentOT=DepOT$num_yes/DepOT$total
colnames(DepOT)[c(1,4)]=c('Department','Percent Overtime')
formattable(DepOT[,c(1,4)])
CS2%>%group_by(OverTime)%>%summarize(count=n())
```

Examining Job Role
```{r}
#job role and satisfaction
CS2cat%>%ggplot(aes(x=JobRole,fill=JobSatisfaction))+
  geom_bar(position='fill')+
  labs(title='Percent Job Satisfaction based on Job Role',
       x='Job Role',
       y='Percent Job Satisfaction')+
  scale_fill_discrete(name='Job Satisfaction')
#job role and education field
CS2cat%>%ggplot(aes(x=JobRole,fill=EducationField))+
  geom_bar(position='fill')+
  labs(title='Percent Education Field based on Job Role',
       x='Job Role',
       y='Percent Education Field')+
  scale_fill_discrete(name='Education Field')
#job role and job involvement
CS2cat%>%ggplot(aes(x=JobRole,fill=JobInvolvement))+
  geom_bar(position='fill')+
  labs(title='Percent Job Involvement based on Job Role',
       x='Job Role',
       y='Percent Job Involvement')+
  scale_fill_discrete(name='Job Involvement')
#job role and job level
CS2cat%>%ggplot(aes(x=JobRole,fill=JobLevel))+
  geom_bar(position='fill')+
  labs(title='Percent Job Level based on Job Role',
       x='Job Role',
       y='Percent Job Level')+
  scale_fill_discrete(name='Job Level')

#job role and years working
CS2%>%ggplot(aes(x=JobRole,y=TotalWorkingYears))+
  geom_boxplot()
#job role and years at company
CS2%>%ggplot(aes(x=JobRole,y=YearsAtCompany))+
  geom_boxplot()
#job role and years in current role
CS2%>%ggplot(aes(x=JobRole,y=YearsInCurrentRole))+
  geom_boxplot()
#job role and age
CS2%>%ggplot(aes(x=JobRole,y=Age,fill=JobRole))+
  geom_boxplot()+
  labs(title='Age Based on Job Role',
       x='Job Role')+
  theme(legend.position='none')
```

Re-Examining attrition
```{r}
#Overtime barplot
CS2%>%ggplot(aes(x=Attrition,fill=OverTime))+
  geom_bar(position='fill')+
  labs(title="Percent of Employees That Worked Overtime Based On Attrition",
       y="Percent")+
  scale_fill_discrete(name="Overtime")
#Age barplot 1
CS2%>%mutate(agefac=cut(Age,breaks=c(10,20,30,40,50,60)))%>%
  ggplot(aes(x=Attrition,fill=agefac))+
  geom_bar(position='fill')+
  labs(title="Percent of Employees' Ages Based On Attrition",
       y="Percent")+
  scale_fill_discrete(name="Age",labels=c("18-20","21-30","31-40","41-50","51-60"))
#Age barplot 2
CS2%>%ggplot(aes(x=Attrition,y=Age,fill=Attrition))+
  geom_boxplot()+
  labs(title='Distribution of Age based on Attrition',
       x='Attrition',
       y='Age')
  
#Job Involvement vs Age barplot
CS2%>%ggplot(aes(x=factor(JobInvolvement),y=Age))+
  geom_boxplot()+
  labs(title="Age based on Job Involvement",
      x="Job Involvement")
#WLB barplot
CS2%>%mutate(WLBFac=as.factor(WorkLifeBalance))%>%ggplot(aes(x=Attrition,fill=WLBFac))+
  geom_bar(position='fill')
#JobRole barplot
CS2%>%ggplot(aes(x=JobRole,fill=Attrition))+
  geom_bar(position='fill')+
  labs(title='Percent Attrition based on Job Role',
       x='Job Role',
       y='Percent Attrition')
#Department barplot
CS2%>%ggplot(aes(x=Department,fill=Attrition))+
  geom_bar(position='fill')+
  labs(title='Percent Attrition based on Department',
       x='Department',
       y='Percent Attrition')
#Job Involvement barplot
CS2%>%ggplot(aes(x=factor(JobInvolvement),fill=Attrition))+
  geom_bar(position='fill')+
  labs(title='Percent Attrition based on Job Involvement',
       x='Job Involvement',
       y='Percent Attrition')
```

Linear Regression
```{r}
CS2salary=CS2cont%>%mutate(Salary=MonthlyIncome*12)

CS2salary%>%ggplot(aes(x=Salary))+geom_histogram()


#Training/Test Split
TrainInd=sample(1:dim(CS2salary)[1],round(0.7*dim(CS2salary[1])))
SalTrain=CS2salary[TrainInd,]
SalTest=CS2salary[-TrainInd,]

SalFit=lm(Salary~.,data=SalTrain)
summary(SalFit)
SalPreds=predict.lm(SalFit,newdata=SalTest)
SalDiffSq=(SalTest$Salary-SalPreds)^2
RMSE=sqrt(sum(SalDiffSq))
RMSE#2.90625e-09
```

By using a Naïve Bayes classification model, examining feature importance, and investigating the Case Study 2 data set, I determined that the three most important features related to attrition were overtime, age, and job role. Using every feature in the data except for ID, employee count, employee number, standard hours, and over18, the Naïve Bayes model was able to predict employee attrition with an accuracy of 0.8352, sensitivity of 0.8447, and specificity of 0.7857. 

Factors related to job role were also examined. Executive positions tended to have higher job levels and ages, while job involvement appeared similar among roles. Finally, using every continuous variable as explanatory variables, a linear regression model was utilized to try to predict salary. The RMSE of this model was 2.90625e-9. I appreciate the opportunity to work on this analysis.

